\documentclass{resume}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage[left=0.35in,top=0.35in,right=0.35in,bottom=0.35in]{geometry}
\newcommand{\tab}[1]{\hspace{.25\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand{\dateentry}[1]{\hfill{\small #1}}
\usepackage{xcolor}

\definecolor{navycustom}{RGB}{40,70,140}
\newcommand{\skill}[1]{\textcolor{navycustom}{#1}}

\name{Alice Paré}
\address{+33 6 87 87 04 89 $|$ alice.pare@gmail.com $|$ linkedin.com/in/alice-pare}

\begin{document}
\vspace*{-0.5em}

\vspace*{-0.5em}
\begin{center}
    \noindent\textbf{Seeking a 6-month internship in Data Science/Generative AI - starting September 2026}
\end{center}
\vspace*{-0.5em}
%----------------------------------------------------------------------------------------
% PROFILE
%----------------------------------------------------------------------------------------
\begin{rSection}{PROFILE}\vspace{-0.3em}
MSc student at CentraleSupélec specializing in Data Science and Machine Learning. Interested in building Generative AI using LLMs, prompt engineering and RAG pipelines to extract insights from unstructured data.
\vspace{-0.3em}
\end{rSection}

\vspace*{-0.5em}

%----------------------------------------------------------------------------------------
% TECH EXPERIENCE
%----------------------------------------------------------------------------------------
\begin{rSection}{TECH EXPERIENCE}\vspace{-0.3em}

{\bf Agile Prototyper} \textsc{- Paris Digital Lab} \dateentry{ Feb 2026 - Jul 2026} \\
Developed 3 MVPs in teams of 3-4 over 7 weeks for companies, covering AI, data, web and IoT.

\vspace{-0.7em} 
\begin{itemize}[label=\scriptsize$\bullet$, left=0.5em, itemsep=0.3em]

    \item \textbf{Real-Time 3D Computer Vision for Nuclear Safety} \textsc{- VINCI Energies} $\mid$ 
    \skill{Python} $\cdot$ 
    \skill{Mediapipe} $\cdot$ 
    \skill{SMPL} \\
    Implemented a real-time deep learning pipeline for 3D human pose estimation using MediaPipe and SMPL models.
Deployed the system on-site to monitor operator posture and provide real-time feedback.

\end{itemize}
\vspace{-0.4em} 

{\bf Teaching Assistant in Computer Science} \textsc{- ESSEC \& CentraleSupélec Bachelor} \dateentry{Sep 2025 - Feb 2026} \\
Designed and led programming tutorials for undergraduate students.
    
\vspace{-0.4em} 
{\bf Student Projects} \textsc{- CentraleSupélec} \dateentry{Sep 2024 -- Feb 2026}
\vspace{-0.4em} 
\begin{itemize}[label=\scriptsize$\bullet$]

    
    \item \textbf{LLM Reasoning Evaluation for Decision Automation} \textsc{- IBM} $\mid$ 
    \skill{Python} $\cdot$ 
    \skill{LLMs} $\cdot$  
    \skill{LangChain} \\
   Evaluated reasoning capabilities of large language models on business decision policies.
Designed benchmarking pipelines using chain-of-thought prompting, multi-agent workflows and logical inference engines.

    \vspace{-0.6em}

    \item \textbf{Satellite Image Classification} $\mid$ 
    \skill{Python} $\cdot$ 
    \skill{Scikit-learn} $\cdot$ 
    \skill{XGBoost} $\cdot$ 
    \skill{GeoPandas} \\
    Built a classification pipeline to predict construction change types from multi-temporal satellite imagery. 
    Engineered 100+ features and benchmarked Random Forest, XGBoost, and stacking ensemble models.

    \vspace{-0.6em}

    \item \textbf{Data-Driven Control} $\mid$ 
    \skill{Python} $\cdot$ 
    \skill{TensorFlow} $\cdot$ 
    \skill{PyTorch} $\cdot$ 
    \skill{Scikit-learn}\\
    Benchmarked RNN, LSTM, and GRU networks against PID, LQR, and MPC controllers for quadrotor trajectory tracking and autonomous landing on a moving vehicle.

    \vspace{-0.6em} 

    \item \textbf{Multi-Drone Exploration} $\mid$ 
    \skill{Python} $\cdot$ 
    \skill{C++} $\cdot$ 
    \skill{PyBullet}\\
    Designed and implemented a decentralized exploration algorithm for autonomous drone swarms.

    \vspace{-0.6em} 

    \item \textbf{Lightweight RAG Tool} $\mid$ 
    \skill{Python} $\cdot$ 
    \skill{Scikit-learn} $\cdot$ 
    \skill{Pandas}\\
    Developed a decision-support system for oncologists using Retrieval-Augmented Generation in collaboration with AI lab MICS.

\end{itemize}

\vspace{-0.6em}
\end{rSection}

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------
\begin{rSection}{EDUCATION}\vspace{-0.3em}

{\bf MEng in Computer Science and Mathematics} \textsc{- CentraleSupélec} \dateentry{ Sep 2024 - Present}
\vspace{-0.7em} 
\begin{itemize} [label=\scriptsize$\bullet$]
    \item Relevant coursework : Machine Learning, Statistics and Learning, High-Performance Computing, Partial Differential Equations, Web Data Intelligence, Algorithm and Complexness, Information Theory.
\end{itemize}
\vspace{-0.4em} 
{\bf Two-year intensive preparatory program} \textsc{- Lycée Louis Le Grand} \dateentry{ Sep 2022 - Jun 2024} 
\vspace{-0.7em} 
\begin{itemize} [label=\scriptsize$\bullet$]
    \item A selective track  in Mathematics \& Computer Science preparing for competitive entrance exams to France’s top engineering schools.
\end{itemize}
\vspace{-0.4em} 
{\bf High-School} \textsc{- Lycée Louis Le Grand} \dateentry{ Sep 2019 - Jun 2022} 
\vspace{-0.7em} 
\begin{itemize} [label=\scriptsize$\bullet$]
    \item French high school “Baccalauréat” diploma, highest honours.
\end{itemize}

\vspace{-0.6em}
\end{rSection}

%----------------------------------------------------------------------------------------
% SKILLS
%----------------------------------------------------------------------------------------
\begin{rSection}{TECH SKILLS}\vspace{-0.3em}

\begin{tabularx}{\linewidth}{@{} >{\bfseries}l X }
Programming & Python, C, OCaml, SQL \\
Libraries & NumPy, PyTorch, Keras, Scikit-Learn, Pandas, PyBullet \\
Tools & Git, Pygame, PostgreSQL\\
Other & Machine Learning, Deep Learning, Reinforcement Learning, Computer Vision \\
\end{tabularx}

\vspace{-0.6em}
\end{rSection}


%----------------------------------------------------------------------------------------
% LANGUAGES
%----------------------------------------------------------------------------------------
\begin{rSection}{Languages}\vspace{-0.3em}
French (native), English (fluent), German (intermediate), Japanese (beginner)
\vspace{-0.6em}
\end{rSection}

%----------------------------------------------------------------------------------------
% EXTRACURRICULARS 
%----------------------------------------------------------------------------------------
\begin{rSection}{EXTRACURRICULARS}\vspace{-0.3em}

\begin{tabularx}{\linewidth}{@{} l X }
Association & Vice-President, Student Council (BDE), CentraleSupélec \\
Sport & National-Level Cheerleading \\
Hackathon & Finalist - Orange Think \& Pitch Hackathon: pitched an AI solution for the future of finance \\
\end{tabularx}


\end{rSection}

\end{document}